\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-09-21 doc/USER_MANUAL/manual_SPECFEM3D.tex
made the description of the force source more precise
moves ABSORB_FREE_SURFACE flag from constants.h.in into ABSORB_INSTEAD_OF_FREE_SURFACE flag in Par_file

@@

@@

\item [{\texttt{COMPONENT\_DIR\_VECT\_SOURCE\_ZUP}}] This parameter specifies the vertical component of 

>>>>

\item [{\texttt{ABSORB\_INSTEAD\_OF\_FREE\_SURFACE}}] Set to \texttt{.true.} to turn on 
absorbing boundary conditions on the top surface which by default constitutes a free surface of the model.

@@

This vector is made unitary internally in the code and thus only its direction matters here;
its norm is ignored and the norm of the force used is \texttt{FACTOR\_FORCE\_SOURCE} times the source time function.

@@

\item [{\texttt{COMPONENT\_DIR\_VECT\_SOURCE\_Z\_UP}}] This parameter specifies the vertical component of 
